### 2019-05-22 4_implementation.tex
Tweak text.

There are also aspects of some systems that we do not consider. For
example, tasks may run on CPUs, GPUs, or any execution resource
supported by a programming system. However, the level of support for
heterogeneous processors varies widely across programming systems (if it exists at all), so
in order to include as many systems as possible in our comparisons, we
evaluate Task Bench only on CPUs in this paper.

@@

We provide two MPI+X implementations of Task Bench to evaluate the
performance of hybrid programming models. Our MPI+OpenMP
implementation uses forall-style parallel loops to execute tasks,
interleaved with MPI point-to-point communication as above. Our
MPI+CUDA implementation follows an offload model where data is copied
to and from the GPU on every timestep.

>>>>

%% There are also aspects of some systems that we do not consider. For
%% example, tasks may run on CPUs, GPUs, or any execution resource
%% supported by a programming system. However, the level of support for
%% heterogeneous processors varies widely across programming systems (if it exists at all), so
%% in order to include as many systems as possible in our comparisons, we
%% evaluate Task Bench only on CPUs in this paper.

@@

We provide two MPI+X implementations of Task Bench to evaluate the
performance of hierarchical programming models. Our MPI+OpenMP
implementation uses forall-style parallel loops to execute tasks,
interleaved with MPI point-to-point communication as above. Our
MPI+CUDA implementation follows an offload model where data is copied
to and from the GPU on every timestep.
